---
title: "Week 1 - Exercise (b)"
output: html_document
author: Océane Follonier
date: 24.09.21
---

## For this part of the exercise, we are to first generate 100 values sampled from a log-normal distribution ($\mu = 1, \sigma = 0.25$), then create a histogram of the distribution (on the normal and log scale). Finally we also want to report the mean and variance of the sample.

### 1. Generate the 100 sampled values

```{r sample}
set.seed(42)
nsamples <- 100
mu <- 1
sigma <- 0.25
x <- rlnorm(n = nsamples, meanlog = mu, sdlog = sigma)
```

### 2. Plot the histogram of the sample

```{r histogram}
hist(x, 
     main="Histogram of samples from log-normal distribution", 
     xlab="Sample (x)")
hist(log(x), 
     main="Histogram on log-normal scale of samples from log-normal distribution", 
     xlab="Sample (log(x))")
```

### 3. Report the mean and variance of the sample

```{r stats}
mean <- mean(x)
variance <- var(x)

mean_log <- mean(log(x))
variance_log <- var(log(x))
```
<u>Using the original samples:</u>

Mean ($\mu$) of the sample: `r mean`

Variance ($\sigma^2$) of the sample: `r variance`

Standard deviation ($\sigma$) of the sample: `r sqrt(variance)`

<u>Using log-transformed samples:</u>

Mean ($\mu$) of the log-transformed sample: `r mean_log`

Variance ($\sigma^2$) of the log-transformed sample: `r variance_log`

Standard deviation ($\sigma$) of the log-transformed sample: `r sqrt(variance_log)`
